Efficient implementation of kernel filtering

### 2007-06-29 article/Article.tex
migale citation
darcs-hash:20070629182722-2fc9d-23f0d9a912eba76ac608c8a4fb11d51fc0fc8c0b.gz
specified seems more english than precised
darcs-hash:20070629191558-2fc9d-174552a8dfe214aa4cbb7da595d12bbcad56519d.gz

All the execution times in this section are measured on a computer with four
Intel\textregistered Xeon\textregistered CPU cores at 2.33GHz with 4MB cache,
running CentOS 4.4 64 bits. Unless precised in the description, the tests are
forced to run on a single core.

@@

\section{Acknowledgments}
We thank Dr Pierre Adenot and MIMA2 confocal facilities
(\url{http://mima2.jouy.inra.fr}) for providing the 3D test image.

\appendix

>>>>

All the execution times in this section are measured on a computer with four
Intel\textregistered Xeon\textregistered CPU cores at 2.33GHz with 4MB cache,
running CentOS 4.4 64 bits. Unless specified in the description, the tests are
forced to run on a single core.

@@

\section{Acknowledgments}
We thank Dr Pierre Adenot and MIMA2 confocal facilities
(\url{http://mima2.jouy.inra.fr}) for providing the 3D test image.
We are grateful to the INRA MIGALE bioinformatics platform
(\url{http://migale.jouy.inra.fr}) for providing the computational resources
used for the timing tests.
\appendix
